Spatial Analysis

### 2022-01-12 Scripts/spatial_analisis.Rmd
Fixed paths after splitting projects

grids_sw <- bind_rows(
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  left_join(land_sf) %>% 
  select(index,state,abrev,lat,lon,spp) %>% 
  mutate(spatial = "sw",
         port_name = NA
         )

grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
) %>%
  mutate(spatial = "fp",
  spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
                 ifelse(spp == "scup", "Stenotomus chrysops", 
                        "Centropristis striata"
                 )
    )
  )

@@

# Ports data
ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  group_by(species_name,state_postal) %>% 
  summarise(n =n()) %>% 
  select(-n)
  # distinct(c(,state_postal), .keep_all = T) # No need for duplication

@@

spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/"))

@@

taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/", name = taxon_read)

>>>>

grids_sw <- bind_rows(
  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  left_join(land_sf) %>% 
  select(index,state,abrev,lat,lon,spp) %>% 
  mutate(spatial = "sw",
         port_name = NA
         )

grids_fp <- my_path("G", "AcrossBoundaries/Data/Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
) %>%
  mutate(spatial = "fp",
  spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
                 ifelse(spp == "scup", "Stenotomus chrysops", 
                        "Centropristis striata"
                 )
    )
  )

@@

# Ports data
ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  group_by(species_name,state_postal) %>% 
  summarise(n =n()) %>% 
  select(-n)
  # distinct(c(,state_postal), .keep_all = T) # No need for duplication

@@

spp_paths <- list.files(my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/"))

@@

taxon_sw <- my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/", name = taxon_read)
